When easy is not preferred: A discounting paradigm to assess load-independent task preference

### 2023-03-07 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
corrected typo

An exploratory was used ANOVA to compare the fit of the final model with a linear random intercept model, confirming that the two models were different from each other ($\chi^2 (`r compare_h2b$Df[2]`)$ = `r compare_h2b$Chisq[2]`, $p<.001$), and with an Akaike Information Criterion of $AIC=`r compare_h2b$AIC[2]`$ and a Bayesian Information Criterion of $BIC=`r compare_h2b$BIC[2]`$ the declining logistic model was superior to the linear model ($AIC=`r compare_h2b$AIC[1]`$, $BIC=`r compare_h2b$BIC[1]`$).
The final model had an effect size of $f^{2}=$ `r round(h2b_level_f2, digits = 2)` for the $n$-back levels and $f^{2}=$ `r round(h2b_dprime_f2, digits = 2)` for $d'$, which are considered large and small, respectively [@Cohen1992].
This means that the $n$-back level explained `r paste0(formatC(h2b_level_f2 * 100, format = "f", digits = 2), "%")` and $d'$ explained `r paste0(formatC(h2b_dprime_f2 * 100, format = "f", digits = 2), "%")` of variance in SVs relative to the unexplained variance, respectively.
The beta coefficient indicated that with every 1-unit increase in $d'$, the SV increased by `r as.numeric(h2b_result.table[3,"Beta"])`.
The effect size of the median RT was $f^{2}=$ `r format(round(h2b_medianRT_f2, digits = 2), nsmall = 2)`.

>>>>

An exploratory ANOVA was used to compare the fit of the final model with a linear random intercept model, confirming that the two models were different from each other ($\chi^2 (`r compare_h2b$Df[2]`)$ = `r compare_h2b$Chisq[2]`, $p<.001$), and with an Akaike Information Criterion of $AIC=`r compare_h2b$AIC[2]`$ and a Bayesian Information Criterion of $BIC=`r compare_h2b$BIC[2]`$ the declining logistic model was superior to the linear model ($AIC=`r compare_h2b$AIC[1]`$, $BIC=`r compare_h2b$BIC[1]`$).
The final model had an effect size of $f^{2}=$ `r round(h2b_level_f2, digits = 2)` for the $n$-back levels and $f^{2}=$ `r round(h2b_dprime_f2, digits = 2)` for $d'$, which are considered large and small, respectively [@Cohen1992].
This means that the $n$-back level explained `r paste0(formatC(h2b_level_f2 * 100, format = "f", digits = 2), "%")` and $d'$ explained `r paste0(formatC(h2b_dprime_f2 * 100, format = "f", digits = 2), "%")` of variance in SVs relative to the unexplained variance, respectively.
The beta coefficient indicated that with every 1-unit increase in $d'$, the SV increased by `r as.numeric(h2b_result.table[3,"Beta"])`.
The effect size of the median RT was $f^{2}=$ `r format(round(h2b_medianRT_f2, digits = 2), nsmall = 2)`.
